---
title: "COVID-19 STATEistics"
resource_files:
- 00_data/CT_states_daily_4pm_et.csv
- 00_data/Global_Mobility_Report.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: bootstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE,
                      collapse = TRUE, comment = "#>")
```

```{r libraries, include=FALSE}
## Load Libraries

# - Data Wrangling
# library(tidyverse)
library(dplyr)       # core wrangling
library(tidyr)       # pivot
library(stringr)     # strings
library(lubridate)   # date object conversion
library(data.table)  # fread, fast handling of data

# - Tables 
library(readr)       # read_csv
library(tibble)      # as_tibble()
library(knitr)       # knit kables
library(kableExtra)  # {r results = 'asis'}

# - Plots
library(ggplot2)     # core plotting
library(scales)      # x,y scales
library(colorspace)  # sequence, diverging colors
library(ggrepel)     # labels, geom_text()
library(plotly)      # interactive plots

# - Math
library(zoo)        # moving average, rollmean

# - URL 
library(RCurl)      # handling links
library(downloader) # wraps `download.file` cross-platform download

# - Shiny
library(shiny)
library(flexdashboard)
```

```{r global, include=FALSE}
## Download Datasets

## 1. The COVID Tracking Project (ct)
link_ct <- "https://api.covidtracking.com/v1/states/daily.csv" 
dest_ct <- paste0(getwd(),"/00_data")
filename_ct <- "CT_states_daily_4pm_et.csv"

# if(!file.exists(file.path(dest_ct, filename_ct))) {
#   download.file(link_ct, file.path(dest_ct, filename_ct))
# }
# --------------------------------------------------
# Comment/Uncomment when updating COVID Tracking data
# download.file(link_ct, file.path(dest_ct, filename_ct)) 

## 2. Google Community Mobility Report (gmcr)
link_gmcr <- "http://www.gstatic.com/covid19/mobility/Global_Mobility_Report.csv?cachebust=57b4ac4fc40528e2"
dest_gmcr <- paste0(getwd(),"/00_data")
filename_gmcr <- "Global_Mobility_Report.csv" # this is the default name from Google

# if(!file.exists(file.path(dest_gmcr, filename_gmcr))) {
#   download.file(link_gmcr, file.path(dest_gmcr, filename_gmcr))
# }
# --------------------------------------------------
# Comment/Uncomment when updating Google data
# download.file(link_gmcr, file.path(dest_gmcr, filename_gmcr))
```

```{r}
## Load Datasets
df_ct <- readr::read_csv(file.path("00_data", filename_ct))
df_gmcr <- data.table::fread(file.path("00_data", filename_gmcr))
df_policy <- readr::read_csv("00_data/states_and_dates_clean.csv")
us_latlong_pop2019 <- readr::read_csv("00_data/us_latlong_pop2019.csv")
```


```{r}
## Data Cleaning

# COVID Tracking Project 
state.abb2 = c(state.abb[1:8], "DC", state.abb[9:50])
state.name2 = c(state.name[1:8], "D.C.", state.name[9:50])

df_ct_clean <- df_ct %>% 
  filter(state %in% state.abb2) %>% 
  mutate(date = ymd(date)) %>% 
  arrange(state, date) %>% 
  
  # Rename columns
  select(date, state, positive, negative, 
         total_tests=totalTestResults, 
         deaths = death,
         daily_cases = positiveIncrease,
         daily_tests = totalTestResultsIncrease,
         daily_deaths = deathIncrease) %>% 
  
  # 5 days because it's the average time between onset and confirmed
  group_by(state) %>% 
  mutate(ave_7d_cases = zoo::rollmean(x=daily_cases, k=7, fill=NA, align='right'),
         ave_7d_tests = zoo::rollmean(x=daily_tests, k=7, fill=NA, align='right'),
         ave_7d_deaths = zoo::rollmean(x=daily_deaths, k=7, fill=NA, align='right')
  ) %>% 
  ungroup() %>%  
  
  # Reorder columns such that: id | cases | tests | deaths
  select(date, state,
         positive, negative, daily_cases, ave_7d_cases, 
         total_tests, daily_tests, ave_7d_tests, 
         deaths, daily_deaths, ave_7d_deaths) %>% 
  
  # Convert 2-letter state abbreviation to full state names:
  left_join(data.frame(state=state.abb2, 
                       state2=state.name2, 
                       stringsAsFactors=FALSE), 
            by=c("state")) %>% 
  select(-state) %>% 
  select(date, state=state2, everything())

# Google Mobility
df_gmcr <- df_gmcr %>% 
  # only include US states
  filter(country_region == "United States") %>% 
  filter(sub_region_1 %in% state.name) %>% 
  filter(sub_region_2 == "") %>% 
  select(-c(country_region_code, country_region, sub_region_2, iso_3166_2_code, census_fips_code, metro_area)) %>%
  rename(state = sub_region_1, 
         `Retail & Recreation` = retail_and_recreation_percent_change_from_baseline,
         `Grocery & Pharmacy` = grocery_and_pharmacy_percent_change_from_baseline,
         `Parks` = parks_percent_change_from_baseline,
         `Transit Stations` = transit_stations_percent_change_from_baseline,
         `Workplaces` = workplaces_percent_change_from_baseline,
         `Residential` = residential_percent_change_from_baseline) %>% 
  mutate(date = lubridate::ymd(date)) %>% 
  as_tibble() %>% 
  tidyr::pivot_longer(-c(state, date), names_to="place", values_to="index") %>% 
  group_by(state, place) %>% 
  # 7 days so we have a week-on-week analysis
  mutate(ave_7d = zoo::rollmean(x=index, k=7, fill=NA, align='right')) %>% 
  ungroup()

# Policy Data
names(df_policy) <- tolower(names(df_policy))

## Republican States
states_gop <- df_policy %>% 
  filter(party == "Republican") %>% 
  pull(state)

## Democrat States
states_dnc <- df_policy %>% 
  filter(party == "Democrat") %>% 
  pull(state)
```

```{r}
# When was ct data last updated?
start_date_ct <- df_ct_clean %>% pull(date) %>% min
end_date_ct <- df_ct_clean %>% pull(date) %>% max

# When was Google Mobility data last updated?
start_date_gmcr <- df_gmcr %>% pull(date) %>% min
end_date_gmcr <- df_gmcr %>% pull(date) %>% max
```

Dashboard {data-orientation=rows}
===========

Inputs {.sidebar}
---------------------------------------------------------------------

```{r}
# Input: US States
selectInput(inputId="state_ct", label="Select a State:",
            choices = c("All States", 
                        "Republican", 
                        "Democrat", 
                        state.name2), 
            selected = "California")

# Input: Date range (start and end)
dateRangeInput(inputId="daterange_ct", label="Date:",
               # Default start at March 1, 2020
               start = "2020-03-01", end = end_date_ct,
               min = start_date_ct, max = end_date_ct)


```

**Last Update**: `r format(end_date_ct, "%b %d, %Y")`

***

Source: [The COVID Tracking Project](https://covidtracking.com/) is a volunteer organization dedicated to collecting and publishing the data required to understand the COVID-19 outbreak in the United States.

***

```{r}
newcasesData <- reactive({
  if(input$state_ct == "All States") {
    df_ct_clean %>% 
      filter(date == input$daterange_ct[2]) %>%
      select(State=state, `New Cases`=daily_cases) %>% 
      arrange(-`New Cases`) %>% 
      mutate(`New Cases` = as.character(`New Cases`))
  }
  else if(input$state_ct == "Republican") {
    df_ct_clean %>% 
      filter(date == input$daterange_ct[2]) %>%
      filter(state %in% states_gop) %>% 
      select(State=state, `New Cases`=daily_cases) %>% 
      arrange(-`New Cases`) %>% 
      mutate(`New Cases` = as.character(`New Cases`))
  }
  else if(input$state_ct == "Democrat") {
    df_ct_clean %>% 
      filter(date == input$daterange_ct[2]) %>%
      filter(state %in% states_dnc) %>% 
      select(State=state, `New Cases`=daily_cases) %>% 
      arrange(-`New Cases`) %>% 
      mutate(`New Cases` = as.character(`New Cases`))
  }
})

renderTable({
  newcasesData()
})
```

```{r}
# Reactive df for summary stats on point data
# - used for value box 
df_vbox_ct <- reactive({
  ## All States
  if(input$state_ct == "All States") {
    df_ct_clean %>% 
      filter(date == input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
  ## Republican 
  else if(input$state_ct == "Republican") {
    df_ct_clean %>% 
      filter(state %in% states_gop) %>% 
      filter(date == input$daterange_ct[2]) %>%  
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )

  }
  ## Democrat
  else if(input$state_ct == "Democrat") {
    df_ct_clean %>% 
      filter(state %in% states_dnc) %>% 
      filter(date == input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
  ## Individual States
  else {
    df_ct_clean %>% 
      filter(state == input$state_ct) %>% 
      filter(date == input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
})
```

Row 
------------------------------------------------------

### New Tests Today
```{r}
renderValueBox ({
  valueBox(
    format(df_vbox_ct()$daily_tests, big.mark=",") 
    # icon="fa-exclamation"
  )
})
```

### New Cases Today
```{r} 
renderValueBox ({
  valueBox(
    format(df_vbox_ct()$daily_cases, big.mark=","),
    #icon="fa-thermometer", 
    color="warning"
  )
})
```

### New Deaths Today
```{r}
renderValueBox ({
  valueBox(
    format(df_vbox_ct()$daily_deaths, big.mark=","), 
    #icon="fa-frown", 
    color="danger"
  )
})
```

Row 3
------------------------------------------------------

### COVID+ Rate
```{r}
renderValueBox ({
  valueBox(
    paste0(100*round(df_vbox_ct()$positive/df_vbox_ct()$total_tests,4),"%"), 
    # icon="fa-user-plus", 
    color="#F8961E"
  )
})

```

### Fatility Rate
```{r}
renderValueBox ({
  valueBox(
    paste0(100*round(df_vbox_ct()$deaths/df_vbox_ct()$positive,4),"%"),
    # icon="fa-bed", 
    color="#F94144"
  )
})

```

Row 4
--------------------

### **DAILY TESTS (vs 7-day MA)**
```{r}
# Reactive df for summary stats on interval time data
# - used for plots 
df_plot_ct <- reactive({
  
  ## All States
  if(input$state_ct == "All States") {
    df_ct_clean %>% 
      filter(date >= input$daterange_ct[1] &
               date <= input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
  ## Republican
  else if(input$state_ct == "Republican") {
    df_ct_clean %>% 
      filter(state %in% states_gop) %>% 
      filter(date >= input$daterange_ct[1] &
               date <= input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
  
  ## Democrat 
  else if(input$state_ct == "Democrat") {
    df_ct_clean %>% 
      filter(state %in% states_dnc) %>% 
      filter(date >= input$daterange_ct[1] &
               date <= input$daterange_ct[2]) %>% 
      group_by(date) %>% 
      summarise(
        total_tests=sum(total_tests), 
        daily_tests=sum(daily_tests),
        ave_7d_tests=sum(ave_7d_tests),
        positive=sum(positive),
        daily_cases=sum(daily_cases),
        ave_7d_cases=sum(ave_7d_cases),
        deaths=sum(deaths),
        daily_deaths=sum(daily_deaths),
        ave_7d_deaths=sum(ave_7d_deaths)
      )
  }
  ## Individual State
  else {
    df_ct_clean %>% 
      filter(state == input$state_ct) %>% 
      filter(date >= input$daterange_ct[1] &
               date <= input$daterange_ct[2])
  }
})

## 1. Daily Tests
renderPlotly ({
  static_plot_tests <- ggplot(data=df_plot_ct(),
                              aes(x = date)) +
    geom_bar(aes(y=daily_tests), stat='identity', fill="dodgerblue2", alpha=0.7) +
    geom_line(aes(y=ave_7d_tests), alpha=0.9, size=1) +
    scale_x_date(
      labels=date_format("%b %d"), date_breaks="3 weeks") +
    scale_y_continuous(
      labels=scales::unit_format(unit="K", scale=1e-3, sep="")) +
    theme_minimal() +
    theme(
      panel.grid.major.x = element_blank(),
      axis.text.x = element_text(size=7, angle=45),
      axis.title = element_blank()
    )
  #print(static_plot_tests)
  ggplotly(static_plot_tests) %>% 
    layout(hovermode='x unified') %>% 
    config(displayModeBar = FALSE)
})


```

### **DAILY CASES (vs 7-day MA)**
```{r}
## 2. Daily Cases
renderPlotly ({
  static_plot_tests <- ggplot(data=df_plot_ct(),
                              aes(x = date)) +
    geom_bar(aes(y=daily_cases), stat='identity', fill="orange2", alpha=0.7) +
    geom_line(aes(y=ave_7d_cases), alpha=0.9, size=1) +
    scale_x_date(
      labels=date_format("%b %d"), date_breaks="3 weeks") +
    # scale_y_continuous(labels=scales::unit_format(unit="K", scale=1e-3, sep="")) +
    theme_minimal() +
    theme(
      panel.grid.major.x = element_blank(),
      axis.text.x = element_text(size=7, angle=45),
      axis.title = element_blank()
    )
  #print(static_plot_tests)
  ggplotly(static_plot_tests) %>% 
    layout(hovermode='x unified') %>% 
    config(displayModeBar = FALSE)
})
```

### **DAILY DEATHS (vs 7-day MA)**
```{r}
## 3. Daily Deaths
renderPlotly ({
  static_plot_tests <- ggplot(data=df_plot_ct(),
                              aes(x = date)) +
    geom_bar(aes(y=daily_deaths), stat='identity', fill="red2", alpha=0.7) +
    geom_line(aes(y=ave_7d_deaths), alpha=0.9, size=1) +
    scale_x_date(
      labels=date_format("%b %d"), date_breaks="3 weeks") +
    # scale_y_continuous(labels=scales::unit_format(unit="K", scale=1e-3, sep="")) +
    theme_minimal() +
    theme(
      panel.grid.major.x = element_blank(),
      axis.text.x = element_text(size=7, angle=45),
      axis.title = element_blank()
    )
  #print(static_plot_tests)
  ggplotly(static_plot_tests) %>% 
    layout(hovermode='x unified') %>% 
    config(displayModeBar = FALSE)
})
```

Trend
======================================================================

Column 
------

```{r}
## Overall Trend
plot_static_newcases <- df_ct_clean %>% 
  select(date, state, daily_cases, ave_7d_cases) %>% 
  mutate(ave_7d_cases = round(ave_7d_cases,0)) %>% 
  rename(Date = date, Ave7d= ave_7d_cases) %>% 
  
  ggplot(aes(x=Date, y=Ave7d)) +
  geom_line(size=0.5, alpha=0.9, col="black") +
  geom_area(alpha=0.1) +
  theme_minimal() +
  facet_wrap(~ state, scales="free_y", nrow=13) +
  scale_x_date(date_labels="%b %d", date_breaks="3 weeks") +
  theme(
    panel.grid=element_blank(),
    axis.title=element_blank(),
    axis.text=element_blank(),
    panel.spacing.x = unit(0.25,"lines"),
    panel.spacing.y = unit(-0.15,"lines"),
    # strip.text.x = element_text(size=8, vjust=-4),
    plot.title=element_text(face="bold", hjust=0.5)
  ) +
  labs(title="Overall Trend of COVID+ Cases")
  
plotly::ggplotly(plot_static_newcases,
                 height=1000, width=1180) %>%
  config(displayModeBar = FALSE)
```

```{r}
## 30-day Trend
plot_static_newcases <- df_ct_clean %>% 
  select(date, state, daily_cases, ave_7d_cases) %>% 
  
  ## Trend for the last 30 days
  filter(date >= end_date_ct-30 & date <= end_date_ct) %>% 
  mutate(ave_7d_cases = round(ave_7d_cases,0)) %>% 
  rename(Date = date, Ave7d= ave_7d_cases) %>% 
  
  ggplot(aes(x=Date, y=Ave7d)) +
  geom_line(size=0.5, alpha=0.9, col="black") +
  geom_area(alpha=0.1) +
  theme_minimal() +
  facet_wrap(~ state, scales="free_y", nrow=13) +
  scale_x_date(date_labels="%b %d", date_breaks="3 weeks") +
  theme(
    panel.grid=element_blank(),
    axis.title=element_blank(),
    axis.text=element_blank(),
    panel.spacing.x = unit(0.25,"lines"),
    panel.spacing.y = unit(-0.15,"lines"),
    # strip.text.x = element_text(size=8, vjust=-4),
    plot.title=element_text(face="bold", hjust=0.5)
  ) +
  labs(title="30-Day Trend of COVID+ Cases")
  
# ggplotly(plot_static_newcases, 
#          height=800, width=800) %>% 
#   # layout(hovermode='x unified') %>% 
#   config(displayModeBar = FALSE)
plotly::ggplotly(plot_static_newcases,
                 height=1000, width=1180) %>%
  config(displayModeBar = FALSE)
```


Mobility {data-orientation=rows}
======================================================================

Inputs {.sidebar}
---------------------------------------------------------------------

```{r}
# Input: US States
selectInput(inputId="state_gmcr", label="Select a State:",
           choices = c("All States", 
                        "Republican", 
                        "Democrat", 
                        datasets::state.name),
            selected = "California")

# Input: Date range (2 - start and end)
dateRangeInput(inputId="daterange_gmcr", label="Date:",
               start = start_date_gmcr, end = end_date_gmcr,
               min = start_date_gmcr, max = end_date_gmcr)


```

**Last Update**: `r format(end_date_gmcr, "%b %d, %Y")`

***

The [Google Mobility Reports](https://www.google.com/covid19/mobility/) show movement trends by area across different categories of places. 

If the line is closer to 0% it means that people are doing similar activities like they did at the beginning of the year.

**Grocery & Pharmacy**:  
- supermarkets, food warehouses, farmers markets, specialty food shops, drug stores, pharmacies 

**Parks**:  
- national parks, beaches, marinas, dog parks, plazas, public gardens

**Residential**:  
- places of residence, houses, apartments

**Retail & Recreation**:   
- restaurants, cafes, shopping centers, theme parks, museums, libraries, movie theaters

**Transit Stations**:  
- public transport hubs, subway, bus, train

**Workplaces**:  
- office space, work districts

Output Value Box 
---------------------------------------------------------------------

```{r}
# Color Palette for 6 places (from coolors.co/palettes)
colorz <- c("#F94144", "#F3722C", "#F9C74F", "#90BE6D", "#43AA8B", "#577590")

# Create a reactive df for valuebox
df_vbox_gmcr <- reactive({
  ## All States
  if(input$state_gmcr == "All States") {
    df_gmcr %>% 
      filter(date == input$daterange_gmcr[2]) %>% 
      group_by(place) %>% 
      summarise(index=median(index, na.rm=TRUE)) %>% 
      ungroup() %>% 
      mutate(index = if_else(index > 0, 
                             paste0("+",as.character(index)), 
                             as.character(index))) %>% 
      pivot_wider(names_from = place, 
                  values_from = index)
    
  }
  ## Republican States
  else if(input$state_gmcr == "Republican") {
    df_gmcr %>%
      filter(state %in% states_gop) %>% 
      filter(date == input$daterange_gmcr[2]) %>%
      group_by(place) %>% 
      summarise(index=median(index, na.rm=TRUE)) %>% 
      ungroup() %>% 
      mutate(index = if_else(index > 0, 
                             paste0("+",as.character(index)), 
                             as.character(index))) %>% 
      pivot_wider(names_from = place, 
                  values_from = index)
  }
  
  ## Democrat States
  else if(input$state_gmcr == "Democrat") {
    df_gmcr %>%
      filter(state %in% states_dnc) %>% 
      filter(date == input$daterange_gmcr[2]) %>%
      group_by(place) %>% 
      summarise(index=median(index, na.rm=TRUE)) %>% 
      ungroup() %>% 
      mutate(index = if_else(index > 0, 
                             paste0("+",as.character(index)), 
                             as.character(index))) %>% 
      pivot_wider(names_from = place, 
                  values_from = index)
  }
  ## Individual States
  else {
    df_gmcr %>% 
      filter(state == input$state_gmcr) %>% 
      filter(date == input$daterange_gmcr[2]) %>% 
      select(place, index) %>% 
      mutate(index = if_else(index > 0, 
                             paste0("+",as.character(index)), 
                             as.character(index))) %>% 
      pivot_wider(names_from = place, 
                  values_from = index)
  }
 
})
```

### Grocery & Pharmacy
```{r}
renderValueBox ({
  valueBox(
    value=paste0(df_vbox_gmcr() %>% pull(`Grocery & Pharmacy`),"%"),
    # color="#4285F4", 
    color=colorz[1],
    icon="fa-shopping-cart"
  )
})
```

### Parks
```{r}
renderValueBox ({
  valueBox(
    paste0(df_vbox_gmcr() %>% pull(`Parks`),"%"), 
    # color="#DB4437", 
    color=colorz[2],
    icon="fa-sun"
  )
})
```

### Residential
```{r}
renderValueBox ({
  valueBox(
    value = paste0(df_vbox_gmcr() %>% pull(`Residential`),"%"), 
    # color = "#F4B400", 
    color=colorz[3],
    icon = "fa-home"
  )
})
```

Value Box Split
----

### Retail & Recreation
```{r}
renderValueBox ({
  valueBox(
    value=paste0(df_vbox_gmcr() %>% pull(`Retail & Recreation`),"%"),
    # color="#4285F4", 
    color=colorz[4],
    icon="fa-store"
  )
})
```

### Transit Stations
```{r}
renderValueBox ({
  valueBox(
    value=paste0(df_vbox_gmcr() %>% pull(`Transit Stations`),"%"),
    # color="#0F9D58", 
    color=colorz[5],
    icon="fa-subway"
  )
})
```

### Workplaces
```{r}
renderValueBox ({
  valueBox(
    value=paste0(df_vbox_gmcr() %>% pull(`Workplaces`),"%"),
    # color="#DB4437", 
    color=colorz[6],
    icon="fa-building"
  )
})
```

Output Plot
---------------------------------------------------------------------

```{r}
# Color Palette for 6 places (from coolors.co/palettes)
colorz <- c("#F94144", "#F3722C", "#F9C74F", "#90BE6D", "#43AA8B", "#577590")

# Filtered Data -- user inputs
filteredData <- reactive({
  
  ## All States
  if(input$state_gmcr == "All States") {
    df_gmcr %>% 
      filter(date >= input$daterange_gmcr[1] &
               date <= input$daterange_gmcr[2]) %>% 
      group_by(date, place) %>% 
      summarise(Mean_Change=mean(index),
                Median_Change=median(index)) %>% 
      rename(Date=date,
             Place=place,
             Change=Median_Change)
  } 
  
  ## Republican States
  else if(input$state_gmcr == "Republican") {
    df_gmcr %>% 
      filter(state %in% states_gop) %>% 
      filter(date >= input$daterange_gmcr[1] &
               date <= input$daterange_gmcr[2]) %>% 
      group_by(date, place) %>% 
      summarise(Mean_Change=mean(index),
                Median_Change=median(index)) %>% 
      rename(Date=date,
             Place=place,
             Change=Median_Change)
  }
  
  ## Democrat States
  else if(input$state_gmcr == "Democrat") {
    df_gmcr %>% 
      filter(state %in% states_dnc) %>% 
      filter(date >= input$daterange_gmcr[1] &
               date <= input$daterange_gmcr[2]) %>% 
      group_by(date, place) %>% 
      summarise(Mean_Change=mean(index),
                Median_Change=median(index)) %>% 
      rename(Date=date,
             Place=place,
             Change=Median_Change)
  }
  ## Individual States
  else {
    df_gmcr %>% 
      filter(state == input$state_gmcr) %>% 
      filter(date >= input$daterange_gmcr[1] &
               date <= input$daterange_gmcr[2]) %>% 
      mutate(ave_7d = round(ave_7d,2)) %>% 
      rename(
        `Date`=date,
        `Place`=place,
        `Change`=index,
        `7d Ave`=ave_7d
      )
  }
})

renderPlotly({
  static_plot <- ggplot(data = filteredData(),
                        aes(x = Date)) +
    geom_hline(yintercept = 0, col="black", size=0.2) + 
    
    ## Actual Values 
    geom_line(aes(y = Change, col = Place), size=0.6) +
    
    ## Smoothed Values 
    # geom_smooth(aes(y=Change, col=Place), size=0.6, se=FALSE) +
    
    ## 7-Day Moving Average
    # geom_line(aes(y = `7d Ave`, col = Place), col="dodgerblue3", size=0.6) +
    
    ## Formatting
    scale_x_date(labels=date_format("%b %d"), date_breaks="3 weeks") +
    scale_y_continuous(labels=function(x) paste0(x,"%")) +
    scale_color_manual(values=colorz) +
    theme_minimal() +
    labs(x="Date", y="% change from baseline", 
         col="Click on each legend<br>to toggle on/off",
         title="Mobility Index") +
    theme(
      # Border
      panel.grid.major = element_blank(),
      axis.line = element_line(colour = "gray"),
      # Text
      axis.text.x = element_text(size=8),
      axis.text.y = element_text(size=10),
      # Labels
      legend.title = element_text(face="italic", size=7, hjust=0),
      plot.title = element_text(face="bold", hjust=0.5, size=11),
      plot.subtitle = element_text(face="italic", hjust=0.5, size=8),
      plot.caption = element_text(face="italic", size=7, hjust=0, margin=margin(t=15))
    )
  ggplotly(static_plot) %>% 
    layout(hovermode='x') %>% 
    config(displayModeBar = FALSE)
  # print(static_plot)
})

```

Map
=================

```{r map data, include=FALSE}
# Shapefile data from `tigris` package
states_shape <- tigris::states(cb=TRUE)

## Create a map dataframe
df_map <- df_ct_clean %>% 
  select(
    date, 
    state_name=state, 
    daily_tests=ave_7d_tests, 
    daily_cases=ave_7d_cases, 
    daily_deaths=ave_7d_deaths, 
    total_deaths=deaths
  ) %>% 
  
  # data cleaning: if NA, then 0; if negative, then positive
  mutate(
    daily_tests = if_else(is.na(daily_tests), 0, daily_tests),
    daily_tests = if_else(daily_tests < 0, -1*daily_tests, daily_tests), 
    daily_cases = if_else(is.na(daily_cases), 0, daily_cases),
    daily_cases = if_else(daily_cases < 0, -1*daily_cases, daily_cases),
    total_deaths = if_else(is.na(total_deaths), 0, total_deaths), 
    daily_deaths = if_else(is.na(daily_deaths), 0, daily_deaths),
    daily_deaths = if_else(daily_deaths < 0, -1*daily_deaths, daily_deaths)
  ) %>% 
  
  # Add population per state
  left_join(us_latlong_pop2019, by="state_name") %>% 
  select(date, state_name, state_abb, everything()) %>% 
  
  mutate(population = population - total_deaths) %>% 
  mutate(
    tests_per_100k = round(100000*daily_tests/population,3),
    cases_per_100k = round(100000*daily_cases/population,3),
    deaths_per_100k = round(100000*daily_deaths/population,3)
  ) %>% 
  mutate(
    popup = str_c(str_c("<b>",state_name,"</b>", sep=""), 
                  str_c("Population: ", format(population, big.mark=","), sep= " "),
                  str_c("Tests/100k: ", tests_per_100k, sep=" "),
                  str_c("Cases/100k:", cases_per_100k, sep=" "),
                  str_c("Deaths/100k: ", deaths_per_100k, sep=" "),
                  sep="<br>")
  ) %>% 
  rename(state = state_name)
```

Inputs {.sidebar}
---------------------------------------------------------------------

##### Date:

```{r}
## Input Selection Tab
fluidPage(
  sliderInput(
    inputId = "daterange_map", label = " ",
    min = start_date_ct, max = end_date_ct,
    value = end_date_ct 
    ## - can't introduce animate until leafletProxy is fixed
    # animate = TRUE 
  )
)

# Reactive filtered data -- ALL
filteredMapPoints <- reactive({
  
  filteredDate <- df_map %>% 
    filter(date == input$daterange_map)
  
  filteredMapPoints <- sp::merge(
    states_shape, 
    filteredDate,
    by.x = "STUSPS", 
    by.y = "state_abb",
    duplicateGeoms=TRUE
  )
})
```

**Last Update**: `r format(end_date_ct, "%b %d, %Y")`

***

According to the [Rockefeller Foundation National Testing Action Plan](https://www.covidexitstrategy.org/), the U.S. needs to initially get to 3 million tests per week, and then 30 million tests per week.

Having a *per 100k* metric is a way to standardize the values for daily testing, confirmed cases, and confirmed deaths per state. 

For example, if the `Test/100k` is 200, it means that for every 100,000 people in that state, there are only 200 people that are getting tested for that day. 

The data table on the right shows which states have the highest number of `Tests/100k`, `Cases/100k`, and `Deaths/100k`. 

The overall goal here is to increase the number of testing and decrease the cases and deaths.

For the average testing numbers per state, refer to the **50 States** tab to see the average testing per state.

***

Map Tabs
------------------------------------

### **MAP - DAILY TESTS**

```{r}
library(leaflet)

renderLeaflet({
  # for some reason, I have to do this to be able to call the dataframe
  filteredMapPoints <- filteredMapPoints()
  
  # remove values from other US territories, converted to NA
  filteredMapPoints <- subset(filteredMapPoints, !is.na(tests_per_100k))

  colorpal_tests <- colorNumeric("Blues",
                                 domain = filteredMapPoints$tests_per_100k)
  
  ## Plot the Map
  filteredMapPoints %>% 
    leaflet() %>% 
    addProviderTiles("CartoDB.DarkMatterNoLabels") %>%
    setView(-99, 40, zoom = 3) %>% 
    
    # Shapefile
    addPolygons(
      fillColor = ~colorpal_tests(tests_per_100k),
      weight = 0.2, fillOpacity=0.8, smoothFactor=0.2, dashArray="2",
      popup = ~popup,
      highlight = highlightOptions(
        color="blue", weight=0.5, dashArray="",
        fillOpacity=0.8, bringToFront=TRUE)
    ) %>%
    
    # Per capita legend
    addLegend(pal = colorpal_tests,
              values = filteredMapPoints$tests_per_100k,
              position = "topright",
              title = "Tests per 100k"
    )
})

```


### **MAP - DAILY CASES**

```{r}
renderLeaflet({
  # for some reason, I have to do this to be able to call the dataframe
  filteredMapPoints <- filteredMapPoints()
  
  # remove values from other US territories, converted to NA
  filteredMapPoints <- subset(filteredMapPoints, !is.na(cases_per_100k))

  colorpal_cases <- colorNumeric("Oranges",
                                 domain = filteredMapPoints$cases_per_100k)
  
  ## Plot the Map
  filteredMapPoints %>% 
    leaflet() %>% 
    addProviderTiles("CartoDB.DarkMatterNoLabels") %>%
    setView(-99, 40, zoom = 3) %>% 
    
    # Shapefile
    addPolygons(
      fillColor = ~colorpal_cases(cases_per_100k),
      weight = 0.2, fillOpacity=0.8, smoothFactor=0.2, dashArray="2",
      popup = ~popup,
      highlight = highlightOptions(
        color="orange", weight=0.5, dashArray="",
        fillOpacity=0.8, bringToFront=TRUE)
    ) %>%
    
    # Per capita legend
    addLegend(pal = colorpal_cases,
              values = filteredMapPoints$cases_per_100k,
              position = "topright",
              title = "Cases per 100k"
    )
})
```

### **MAP - DAILY DEATHS**

```{r}
renderLeaflet({
  # for some reason, I have to do this to be able to call the dataframe
  filteredMapPoints <- filteredMapPoints()
  
  # remove values from other US territories, converted to NA
  filteredMapPoints <- subset(filteredMapPoints, !is.na(deaths_per_100k))

  colorpal_deaths <- colorNumeric("Reds",
                                  domain = filteredMapPoints$deaths_per_100k)
  
  ## Plot the Map
  filteredMapPoints %>% 
    leaflet() %>% 
    addProviderTiles("CartoDB.DarkMatterNoLabels") %>%
    setView(-99, 40, zoom = 3) %>% 
    
    # Shapefile
    addPolygons(
      fillColor = ~colorpal_deaths(deaths_per_100k),
      weight = 0.2, fillOpacity=0.8, smoothFactor=0.2, dashArray="2",
      popup = ~popup,
      highlight = highlightOptions(
        color="red", weight=0.5, dashArray="",
        fillOpacity=0.8, bringToFront=TRUE)
    ) %>%
    
    # Per capita legend
    addLegend(pal = colorpal_deaths,
              values = filteredMapPoints$deaths_per_100k,
              position = "topright",
              title = "Deaths per 100k"
    )
})
```


Data Tables {data-width=300}
--------------------------------------------

### **TABLE - DAILY TESTS**
```{r}
# Data Table: Tests per 100k
renderTable({
  filteredMapPoints()@data %>%
    select(State=state, `Tests/100k`=tests_per_100k) %>% 
    arrange(desc(`Tests/100k`)) %>% 
    filter(!is.na(`Tests/100k`))
})
```

### **TABLE - DAILY CASES**
```{r}
# Data Table: Cases per 100k
renderTable({
  filteredMapPoints()@data %>%
    select(State=state, `Cases/100k`=cases_per_100k) %>% 
    arrange(desc(`Cases/100k`)) %>% 
    filter(!is.na(`Cases/100k`))
})
```

### **TABLE - DAILY DEATHS**
```{r}
# Data Table: Deaths per 100k
renderTable({
  filteredMapPoints()@data %>%
    select(State=state, `Deaths/100k`=deaths_per_100k) %>% 
    arrange(desc(`Deaths/100k`)) %>% 
    filter(!is.na(`Deaths/100k`))
})
```

About
======================================================================

Column 1
--------------------------------------------

#### COVID Tracking Project

The [COVID Tracking Project](https://www.covidtracking.com) gathers testing information from different sources for all 50 states. This was used in determining the number of total tests, number of positive and negative cases, and many more information. See the link for data schema. 

```{r}
data.frame(
  Column = c("state", "date", "positive", "negative", "total_tests", "deaths"),
  Description = c("U.S. State", "Date of Reporting", 
                  "Number of confirmed COVID-19 cases, as reported by different health data sources", 
                  "Derived from the number of tests minus the number of positive cases",
                  "Total number of tests", "Total number of deaths")
) %>% 
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Google Community Mobility Reports

The [Community Mobility Reports](https://www.google.com/covid19/mobility/) show movement trends by region, across different categories of places. For this particular visualization the data was subsetted only for the United States. Note that location accuracy and the understanding of categorized places varies from region to region, so Google does not recommend using the data to compare changes between countries, or between regions with different characteristics (e.g. rural versus urban areas). 

In short, the graph is an indicator if Americans are going back to their normal routines earlier this year. If the blue line is closer to the baseline, 0%, it means that people in that area are doing similar activities like they did in January. 

The data shows visitors to (or time spent in) categorized places change compared to the **baseline** days. A baseline day represents a *normal* value for that day of the week, in this case it is the median value from the 5-week period from January 3rd to February 6th 2020. Each location visit is classified into 6 categories:

```{r}
data.frame(
  Location = c("Retail & Recreation",
               "Grocery & Pharmacy",
               "Parks",
               "Transit Stations",
               "Workplaces",
               "Residential"),
  Description = c("mobility trends for places like restaurants, cafes, shopping centers, theme parks, museums, libraries, and movie theaters",
                "mobility trends for places like grocery markets, food warehouses, farmers markets, specialty food shops, drug stores, and pharmacies",
                  "mobility trends for places like national parks, public beaches, marinas, dog parks, plazas, and public gardens",
                  "mobility trends for places like public transport hubs such as subway, bus, and train stations",
                  "mobility trends for places of work",
                  "mobility trends for places of residence")
) %>% 
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

***

#### About the Author

My name is **Jericho** and I created this Shiny app for educational and informational purposes only. 

All datasets used and information provided are publicly available online. 

Please check my other work at [**GitHub**](https://github.com/neooooo28) and connect with me on [**LinkedIn**](https://www.linkedin.com/in/jerichovillareal/)! 



